---
title: "Investment Report"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc_float: 
      collapsed: FALSE
      smooth_scroll: FALSE
    toc: true
    toc_depth: 3
---

<style>
#TOC {
  color: #708090;
  font-family: Calibri;
  font-size: 16px; 
  border-color: #708090;
}
h1.title {
  color: #F08080;
  background-color: #F5F5F5;
  opacity: 0.6;
  font-family: Calibri;
  font-size: 20px;
}
h4.author {
  color: #708090;
  font-family: Calibri;
  background-color: #F5F5F5;
}
h4.date {
  color: #708090;  
  font-family: Calibri;
  background-color: #F5F5F5;
}
body {
  color: #708090;
  font-family: Calibri;
  background-color: #F5F5F5;
}
pre {
  color: #708090;
  background-color: #F8F8FF;
}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.align = 'center', out.width = '80%', echo = TRUE)
```

### Loading libraries and the dataset
```{r data, message = FALSE}
require(tidyverse)
require(dplyr)
require(ggplot2)
library(knitr) 

investment_annual_summary <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/d0251f26117bbcf0ea96ac276555b9003f4f7372/investment_annual_summary.csv")

investment_services_projects <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/bcb2e39ecbe521f4b414a21e35f7b8b5c50aec64/investment_services_projects.csv")

```

The `investment_annual_summary` dataset provides a summary of the dollars in millions provided to each of the following regions for each fiscal year, from 2012 to 2018:

- East Asia and the Pacific
- Europe and Central Asia
- Latin America and the Caribbean
- Middle East and North Africa
- South Asia
- Sub-Saharan Africa

```{r investment-annual-summary, out.width = '85%', fig.cap = 'Figure 1.1 The Investment Annual Summary for each region for 2012 to 2018'}

ggplot(investment_annual_summary, 
       aes(x = fiscal_year, y = dollars_in_millions, 
       color = region)) +
  geom_line() +
  labs(
    title = "Investment Annual Summary",
    x = "Fiscal Year",
    y = "Dollars in Millions"
  )
```


### Investment Projects in Brazil

The `investment_services_projects` dataset provides information about each investment project from 2012 to 2018. Information listed includes the project name, company name, sector, project status, and investment amounts.

```{r brazil-investment-projects, out.width= '95%', fig.cap = 'Figure 1.2 The Investment Services Projects in Brazil from 2012 to 2018'}

brazil_investment_projects <- investment_services_projects %>%
  filter(country == "Brazil") 

ggplot(brazil_investment_projects, 
       aes(x = date_disclosed, y = total_investment, 
       color = status)) +
  geom_point() +
  labs(
    title = "Investment Services Projects",
    x = "Date Disclosed",
    y = "Total IFC Investment in Dollars in Millions"
  )
```


### Investment Projects in Brazil in 2018

```{r brazil-investment-projects-2018, out.width = '95%', fig.cap = 'Figure 1.3 The Investment Services Projects in Brazil in 2018'}

brazil_investment_projects_2018 <- investment_services_projects %>%
  filter(country == "Brazil",
         date_disclosed >= "2017-07-01",
         date_disclosed <= "2018-06-30")

ggplot(brazil_investment_projects_2018, 
      aes(x = date_disclosed, y = total_investment, color = status)) +
      geom_point() +
      labs(
        title = "Investment Services Projects in Brazil in 2018", 
        x = "Date Disclosed", 
        y = "Total IFC Investment in Dollars in Millions"
      )
```



